---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
suppressPackageStartupMessages({
  library(AnVIL)
})
```

## Inputs for this workflow
```{r}
fpath <- "gs://fc-07ee4ddc-5b5b-46f6-bed7-809aa14bb012/IBDMDB/ibdmdb_file_list.txt"
inputs <- read.table(gsutil_pipe(fpath), sep = "\t")
inputs
```

Extract sample names from input file names
```{r}
sampleName <- gsub("_R1.fastq.gz", "", basename(inputs$V1))
```


## Setup correct workspace
```{r}
avworkspace_namespace("waldronlab-terra-rstudio")
avworkspace_name("mtx_workflow_biobakery_ver3")
```

```{r}
avbucket()
```

## Collect output `.tsv` files
It seems like that `avworkflow_files` function accesses the most recent job. I can
specify a specific submission, which can be found using `avworkflow_jobs()`.

```{r}
avworkflow_jobs()
```


### Available outputs from the current workflow
- genefamilies_relab   
- pathabundance_relab    
- pathcoverage   

```{r}
outputs <- avworkflow_files()

ind <- grep(".tsv", outputs$file)
outputs$file[ind]
```

Copy workflow outputs in a file system to apply `make_data`
```{r}

```








```{r warning=FALSE}
output_ind <- 63
output_path <- outputs$path[output_ind]
res <- read.table(gsutil_pipe(output_path), sep = "\t")
head(res)
```

```{r warning=FALSE}
output_name <- "humann_pathabundance_relab_counts.tsv"
output_ind <- which(outputs$file == output_name)
output_path <- outputs$path[output_ind]

relab_counts <- read.table(gsutil_pipe(output_path))
relab_counts
```

```{r warning=FALSE}
output_name <- "HSM7J4NY_pathabundance_relab.tsv"
output_ind <- which(outputs$file == output_name)
output_path <- outputs$path[output_ind]

HSM7J4NY_abundance <- read.table(gsutil_pipe(output_path), sep = "\t")
head(HSM7J4NY_abundance)
```
